---
title: "Mechanistic temperature-size rule explanation should reconcile physiological and mortality responses to temperature "
author: "Shane A. Richards and Asta Audzijonyte"
date: "29/03/2022"
output:
  html_document:
    highlight: tango
    theme: cerulean
    toc: yes
    toc_float: no
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r message=FALSE, warning=FALSE}
rm(list = ls()) # clear memory

library(tidyverse)
library(tibble)
library(ggplot2)
library(cowplot)
library(tidyr)
```

# Useful functions

```{r}
# Reserve:Structure ratio 
RSRatio <- function(age) {
  tmp <- rs1*(age-a_bar)
  tmp <- max(tmp, -20) # bound below
  tmp <- min(tmp,  20) # bound above

  return(rs_min + (rs_max - rs_min)*exp(tmp) / (1.0 + exp(tmp)))
} 

# Predator length [m]
predatorLength <- function(S) {
  return((S/l_const)^(1/3.0)) # assumes invariant growth
} 

# Mortality rate [d-1]
mortProb <- function(l) {
  m_rate <- m_min + (m_max-m_min)*exp(-m1*l) # instantaneous mortality rate
  return(1.0 - exp(-m_rate)) # probability die per day
} 

# intake rate [d d-1] 
# Egle - extended to include temperature
grossIntake <- function(S) {
  Eiscalar <- exp((-Ei/k)*(1/Temp-1/Tref))
  
  return((g0*S^g1)*Eiscalar*S^(ci*(Temp-Tref)))
}

# DEB maintenance version [g d-1 g-1]
# Egle - extended to include temperature
maintenance <- function(S, R) {
  Emscalar <- exp((-Em/k)*(1/Temp-1/Tref))
  
  # return((ms*S + mr*w*R)*Emscalar*(S+R)^(cm*(Temp-Tref)))
  return((ms*S + mr*R)*Emscalar*(S+R)^(cm*(Temp-Tref)))
}

# Energetic reproductive cost
reproCost <- function(S) {
  return(ra*S^rb)
}

# scaling factor
phi <- function(Temp, Tref, m, x) {
  if (x == "I") { # Intake
    Eiscalar <- exp((-Ei/k)*(1/Temp-1/Tref))
    Val      <- Eiscalar * m^(ci*(Temp - Tref))
  } else { # Maintenance
    Emscalar <- exp((-Em/k)*(1/Temp-1/Tref))
    Val      <- Emscalar * m^(cm*(Temp - Tref))
  }
  
  return(Val)
}
```

# Model parameters for baseline scenario

```{r message=FALSE, warning=FALSE}
# Model parameters for the baseline zero fishing scenario 
max_age_years <- 20      # years of simulation
max_age_days  <- 365*max_age_years # (d)

rs_max  <- 1.3           # maximum RS ratio
rs_min  <- 0.0           # minimum RS ratio

# length-weight conversion: 
l_const <- 1250/(0.60^3) # (g m-1) num = weight (g), denom = length (m)
# length-weight conversion uses weight of S only and assumes that 
# 1250g of S weight (ca 3000g of total) corresponds to 60cm long fish

g0      <- 0.1           # intake rate constant: intake when structural weight
                         #   is 1 g (g d-1), includes assimilation efficiency 
g1      <- 0.6667        # power to uptake rate with S weight

ms      <- 0.003         # maintenance cost of structural mass (g d-1 g-1)
mr      <- 0.0003        # maintenance cost of reversible mass (g d-1 g-1)  

s_eff   <- 0.3333        # conv. efficiency of assimilated intake to structure
r_eff   <- 0.9           # conv. efficiency of assimilated intake to reversible

# Reproductive cost function 
ra      <- 6             # reprod cost for 1 g of struct weight: (g g-1)
rb      <- 0.6           # reprod cost power w.r.t. structural weight

# Mortality parameters 
#m_min   <- 0.2/365      # background mortality rate (d-1) 

# m1                    # steepness of the length-dependent mortality rate
m_max   <- 4/365        # max length-dependent mortality rate (d-1)

s1      <- 7.0          # steepness of the condition related mortality rate
s_max   <- 4/365        # maximum condition related rate (d-1) [when R = 0]

 #Fishing mortality parameters 
# Egle - F changed to 0
Fm   <- 0               # Instantaneous fishing mortality (day-1)
Fmid <- 0.3             # length (in meters) of the 50% fishing selectivity
Fk   <- 20              # steepness of the logistic fishing function 

# Egle - temperature parameters added 

# These are important - we are looking at growth changes after 3C of warming
Temp <- 283              # ambient temperature, in Kelvin
Tref <- 280              # reference temperature, in Kelvin
k    <- 0.00008617332    # Boltzman constant 
```

# Scenarios

```{r}
#different scenarios with already optimised parameters (in excel)  
scen_par <- read.csv(file="Scenarios3.csv", header=TRUE, sep=",",
  dec=".") 
nscen <- length(scen_par$Sc)

scen_used <- read.csv(file="FinalScenarioNos.csv", header=FALSE, fileEncoding="UTF-8-BOM", sep=",",
  dec=".") 
names(scen_used) <- "Sc_int"
# number of scenarios
scen_used <- scen_used %>%
  mutate(Sc = paste("Sc", as.character(Sc_int), sep = ""))
nscen_used <- length(scen_used$Sc)
scen_used$Sc_new <- 1:nrow(scen_used)

# create global scenario variables extracted from scenario 
Em <- 0.0
Ei <- 0.0
cm <- 0.0
ci <- 0.0
m1 <- 0.0
m_min <- 0.0
# create global optimal LH-variables extracted from scenario 
rs1   <- 0.0
a_bar <- 0.0
w     <- 0.0

GetScenario <- function(Sc) {
  rw <- which(scen_par$Sc == Sc)
  
  Em <<- scen_par$Em[rw[1]]
  Ei <<- scen_par$Ei[rw[1]]
  cm <<- scen_par$cm[rw[1]]
  ci <<- scen_par$ci[rw[1]]
  m1 <<- scen_par$m1[rw[1]]
  m_min <<- scen_par$m_min[rw[1]]
  
  rs1   <<- scen_par$rs1[rw[1]]
  a_bar <<- scen_par$a_bar[rw[1]]
  w     <<- scen_par$w[rw[1]]

  return(length(rw) == 0) # found a valid scenario
}

GetScenario_new <- function(Sc_new) {
  rw <- which(scen_par$Sc == scen_used$Sc[Sc_new])
  
  Em <<- scen_par$Em[rw[1]]
  Ei <<- scen_par$Ei[rw[1]]
  cm <<- scen_par$cm[rw[1]]
  ci <<- scen_par$ci[rw[1]]
  m1 <<- scen_par$m1[rw[1]]
  m_min <<- scen_par$m_min[rw[1]]
  
  rs1   <<- scen_par$rs1[rw[1]]
  a_bar <<- scen_par$a_bar[rw[1]]
  w     <<- scen_par$w[rw[1]]

  return(length(rw) == 0) # found a valid scenario
}
```

## turn off life-history optimisation

```{r eval = TRUE}
# This code turns off selection and uses the base-line allocation strategy 
#   for all scenarios

# do_not_optimise_new <- c(4,15,17,28)
# do_not_optimise_old <- scen_used$Sc_int[do_not_optimise_new]

## if you want to run scnenarios without life-history optimisation, uncomment lines below
# do_not_optimise_old <- 2:nrow(scen_par)
# scen_par$rs1[do_not_optimise_old] <- scen_par$rs1[1]
# scen_par$a_bar[do_not_optimise_old] <- scen_par$a_bar[1]
# scen_par$w[do_not_optimise_old] <- scen_par$w[1]
```

# Fig. 3: scaling of rates

```{r}
GetScenario_new(17)

TC     <- 7:10
Temp_v <- TC + 273

# Egle - extended to include temperature
Eiscalar_v <- exp((-Ei/k)*(1/Temp_v-1/Tref))
Emscalar_v <- exp((-Em/k)*(1/Temp_v-1/Tref))

df_temperature <- tibble(
  Temperature = TC,
	Intake      = Eiscalar_v,
	Metabolism  = Emscalar_v
) %>%
gather(key = "Process", value = "Scalar", 2:3)

p1 <- ggplot(df_temperature) +
	geom_line(aes(x = Temperature, y = Scalar, color = Process)) +
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  ylim(1,1.4) +
  labs(
    x = expression("Temperature ("*~degree*C*")"),
    y = expression("Scalar, "*phi)) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    legend.position = "none")
p1
```

```{r}
mass_min <- 1    # minimum mass to plot (g)
mass_max <- 1000 # maximum mass to plot (g)
mass_n   <- 20   # masses to plot

m <- mass_min*((mass_max/mass_min)^((1:mass_n - 1)/(mass_n-1)))

scenarios <- c(17, 19, 28) # original scenario

v_scen <- NULL
v_type <- NULL
v_mass <- NULL
v_phi  <- NULL

for (i in scenarios) {
  GetScenario_new(i)
  
  v_scen <- c(v_scen, rep(i, mass_n))
  v_type <- c(v_type, rep("Intake", mass_n))
  v_mass <- c(v_mass, m)
  v_phi  <- c(v_phi, phi(Temp, Tref, m, "I"))
  
  v_scen <- c(v_scen, rep(i, mass_n))
  v_type <- c(v_type, rep("Metabolism", mass_n))
  v_mass <- c(v_mass, m)
  v_phi  <- c(v_phi, phi(Temp, Tref, m, "M"))
}

df_phi <- tibble(
    Sc = v_scen, type = v_type, mass = v_mass, phi = v_phi
  ) %>% mutate(
    grp = paste(Sc, type, sep = "_")
  )
```

```{r}
p2 <- ggplot(df_phi) +
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(aes(x = mass, y = phi, color = type, 
    linetype = factor(Sc), group = grp)) +
  labs(
    x = "Mass (g)", y = expression("Scalar, "*phi), 
    color = "Process", linetype = "Scenario") +
  ylim(0.9,1.8) +
  theme_bw() +
  theme(panel.grid = element_blank())
```

```{r}
plot_grid(p1, p2, labels = c("A", "B"), rel_widths = c(1,1.5))
```

### ### 

# Main loop: scenario predictions

```{r}
# useful age-dependent values
Res               <- array(data=0,c(max_age_years,365, nscen_used))
Str               <- array(data=0,c(max_age_years,365, nscen_used))
dayIntake         <- array(data=0,c(max_age_years,365, nscen_used))
dayMaintenance    <- array(data=0,c(max_age_years,365, nscen_used))
dayNetIntake      <- array(data=0,c(max_age_years,365, nscen_used))
dayLambda         <- array(data=0,c(max_age_years,365, nscen_used))
dayPredatorLength <- array(data=0,c(max_age_years,365, nscen_used))
daySurvival       <- array(data=0,c(max_age_years,365, nscen_used))
yearSpawn         <- array(data=0,c(max_age_years, nscen_used))
yearRepCost       <- array(data=0,c(max_age_years, nscen_used))
yearFitness       <- array(data=0,c(max_age_years, nscen_used))
natmortality      <- array(data=0,c(max_age_years,365, nscen_used))
fishmortality     <- array(data=0,c(max_age_years,365, nscen_used))
dayGrowth         <- array(data=0,c(max_age_years,365, nscen_used))
relGrowth         <- array(data=0,c(max_age_years,365, nscen_used))
strGrowth         <- array(data=0,c(max_age_years,365, nscen_used))

for (aa in 1: nscen_used) { # aa is the scenario number
  a1 <- which(scen_par$Sc == scen_used$Sc[aa])[1]
  # extract scenario patrameters and optimal LH
  Em <- scen_par$Em[a1]
  Ei <- scen_par$Ei[a1] 
  cm <- scen_par$cm[a1]
  ci <- scen_par$ci[a1] 
  m1 <- scen_par$m1[a1]
  m_min <- scen_par$m_min[a1]
  
  Eiscalar <- exp((-Ei/k)*(1/Temp-1/Tref))
  Emscalar <- exp((-Em/k)*(1/Temp-1/Tref))
  
  rs1   <- scen_par$rs1[a1]  
  a_bar <- scen_par$a_bar[a1]
  w     <- scen_par$w[a1]
  
  # set initial weight
  S0 <- 1             # initial weight 
  R0 <- S0*RSRatio(0) # enforce correct initial reserve-structural ratio
  S0 <- 1/(1+RSRatio(0))
  R0 <- RSRatio(0) *S0

	# set day 1 year 1 mass
  Res[1,1,aa] <- R0
  Str[1,1,aa] <- S0

  daySurvival[1,1,aa] <- 1.0 # initially all individuals are alive  

  # perform the simulation
  for (yr in 1:max_age_years) { # for each year
     for (day in 1:364) { # for each day
      Rstart <- Res[yr,day,aa] # starting mass (reserve)
      Sstart <- Str[yr,day,aa] # starting mass (structure)
    
      # calc length using str
      dayPredatorLength[yr,day,aa] <- (Sstart/l_const)^(1/3.0) 
      fish_mort <- Fm / (1+exp(-Fk*(dayPredatorLength[yr,day,aa]-Fmid)))
      mort_rate <- m_min + 
      	(m_max-m_min)*exp(-m1*dayPredatorLength[yr,day,aa]) + # predation
        s_max*exp(-s1*Rstart/Sstart)   +                      # starve
        fish_mort                                             # fishing
      
      fishmortality[yr,day+1,aa] <- fish_mort   
      mort_prob <- 1.0 - exp(-mort_rate) # probability die this day
      # prob alive
      daySurvival[yr,day+1,aa] <- (1-mort_prob)*daySurvival[yr,day,aa] 
      natmortality[yr,day+1,aa] <- m_min + 
      	(m_max-m_min)*exp(-m1*dayPredatorLength[yr,day,aa]) + # predation
        s_max*exp(-s1*Rstart/Sstart)                          # starve

      # temperature-dependent intake
      intake <- g0*Sstart^g1 * 
      	Eiscalar * Sstart^(ci*(Temp-Tref))
    
      respiration <- (ms*Sstart + mr*Rstart) * 
      	Emscalar * (Sstart + Rstart)^(cm*(Temp-Tref)) # (g d-1)
      net_intake  <- intake - respiration             # (g d-1)

      dayIntake[yr, day,aa]      <- intake
      dayMaintenance[yr, day,aa] <- respiration
      dayNetIntake[yr, day,aa]   <- net_intake
      age                        <- 365*(yr-1) + day # age of animal (days)
      
      # add bounds to prevent numerical issues when calculating lambda
      tmp <- rs1*(age-a_bar)
      tmp <- max(tmp, -20) # bound below
      tmp <- min(tmp,  20) # bound above
      dayLambda[yr, day,aa] <- rs_min + (rs_max - rs_min)*exp(tmp) /
        (1.0 + exp(tmp)) # RS ratio = strategy
    
      if (net_intake >= 0) {
        dR <- r_eff*net_intake # maximum R allocation
        dS <- s_eff*net_intake # maximum S allocation
        # use Lambdamax instead of dayLambda and set w=1  
        if (dayLambda[yr, day,aa]*Sstart > Rstart) { # need to bump up reserves
          r_take <- min(dayLambda[yr, day,aa]*Sstart - Rstart, dR) 
          Rstart <- Rstart + r_take
          net_intake <- net_intake - r_take/r_eff
        } else { # need to bump up structure
          s_take <- min(Rstart/dayLambda[yr, day,aa] - Sstart, dS) 
          Sstart <- Sstart + s_take
          net_intake <- net_intake - s_take/s_eff
        }
        
        # partition remaining mass to keep desired ratio
        Res[yr,day+1,aa] <- Rstart + dayLambda[yr, day,aa] * r_eff * s_eff *
        	net_intake / (r_eff + dayLambda[yr, day,aa]*s_eff) 
        Str[yr,day+1,aa] <- Sstart + r_eff*s_eff*net_intake / 
        	(r_eff +     dayLambda[yr, day,aa]*s_eff)       
      } else {
      	# what should be taken from R given the conversion inefficiencies 
        dR <- (1/r_eff)*net_intake 
        newR <- (Rstart + dR)
        if (newR < 0) {
          newR <- 0
        }
     
        Res[yr,day+1,aa] <- newR
        Str[yr,day+1,aa] <- Sstart
      }  

      # percentage change in weight over the day
      Growth <- (Res[yr,day+1,aa]+Str[yr,day+1,aa]) -
      	(Res[yr,day,aa]+Str[yr,day,aa]) 
      percGrowth           <- (Growth/(Res[yr,day,aa]+Str[yr,day,aa])) * 100
      sGrowth              <- Growth/Str[yr,day,aa] * 100
      dayGrowth[yr,day,aa] <-  Growth
      relGrowth[yr,day,aa] <- percGrowth
      strGrowth[yr,day,aa] <- sGrowth
    }

    dayPredatorLength[yr,365,aa] <- dayPredatorLength[yr,364,aa]
    dayGrowth[yr,365,aa]         <- dayGrowth[yr,364,aa]
    relGrowth[yr,365,aa]         <- relGrowth[yr,364,aa]
    strGrowth[yr,365,aa]         <- strGrowth[yr,364,aa]

    # perform spawning
    repro_cost <- ra*Str[yr,365,aa]^rb # fixed cost of reproduction
    # spawning mass after cost
    spawn_mass <- max(0, w*Res[yr,365,aa] - repro_cost) 
  
    if (spawn_mass > 0) { # enough to spawn?
      Res[yr,365,aa]     <- Res[yr,365,aa] - spawn_mass - repro_cost
      yearSpawn[yr,aa]   <- spawn_mass
      yearRepCost[yr,aa] <- repro_cost
      yearFitness[yr,aa] <- spawn_mass*daySurvival[yr,365,aa]
    } 
  
    if (yr < max_age_years) {
      Str[yr+1,1,aa]         <- Str[yr,365,aa]
      Res[yr+1,1,aa]         <- Res[yr,365,aa]
      daySurvival[yr+1,1,aa] <- daySurvival[yr,365,aa]
      natmortality[yr+1,1,aa]  <- natmortality[yr,365,aa]
      fishmortality[yr+1,1,aa]  <- fishmortality[yr,365,aa]
    }
  }
}
```

# Fitness

```{r}
## Fitnesses of all scenarios
v_LifetimeFitness <- apply(yearFitness, 2, sum) # expected life-time fitness
df_LifetimeFitness <- tibble(
	Sc = scen_used$Sc,
	LifetimeFitness = v_LifetimeFitness
) %>%
left_join(scen_used, by = "Sc")

ggplot(df_LifetimeFitness) +
	geom_point(aes(x = Sc_new, y = LifetimeFitness)) +
	theme_bw() +
	labs(y = "Expected lifetime spawning biomass") +
	theme()
```

# make scenario dataframe

```{r fig.width=9, fig.height=7}
param_value <- NULL
param_type  <- NULL
age         <- NULL
scenario    <- NULL
baseline    <- NULL

#if plotting for first 8 years uncomment this
#max_age_years <- 8

# calculate year of maturation
maturation_age <- rep(1, nscen_used)
for (i in 1:nscen_used) {
  for (j in 1:max_age_years) {
   	if (yearSpawn[j,i] == 0) {
   	  maturation_age[i] <- maturation_age[i] + 1
   	}
  }
}

# create some useful summary statistics
scen_par <- scen_par %>%
	mutate(
		Em_gt_Ei = Em > Ei,
		cm_gt_ci = cm > ci
	)

df_scenario <- tibble(
  scenario = scen_used$Sc_int,
	maturation_age = maturation_age
)
df_scenario$Em_gt_Ei <- scen_par$Em_gt_Ei[scen_used$Sc_int]
df_scenario$cm_gt_ci <- scen_par$cm_gt_ci[scen_used$Sc_int]
df_scenario$m1 <- scen_par$m1[scen_used$Sc_int]
df_scenario$m1 <- factor(df_scenario$m1)

# create a large age-length relation for each scenario
for (aa in 1: nscen_used) { # for each scenario
  for (yr in 1:max_age_years) { # for each year
    param_value <- c(param_value, dayPredatorLength[yr, ,aa]) # save reserves
    age         <- c(age, 1:365 + 365*(yr-1))            # add next year
    param_type  <- c(param_type, rep("Reversible", 365)) # add parameter
    scenario    <- c(scenario, rep(scen_used$Sc_int[aa],365))              # add scenario
  }
}

# place values into a data frame
df_length <- tibble(
	age = age, 
	type = param_type, 
	value = param_value, 
	scenario = scenario
) %>%
left_join(df_scenario, by = "scenario")

df_length$maturation_age <- factor(df_length$maturation_age)

# create a reference data set and scenario data set
df_baseline <- filter(df_length, scenario == "1") %>%
	dplyr::select(-scenario)
df_other    <- filter(df_length, scenario != "1")
names(df_other)[4] <- "Sc_int"
df_other <- left_join(df_other, scen_used, by = "Sc_int")

rm(df_length) # don't need this now
```

### ### 
# Plots

## Baseline scenario growth 
(not needed)

```{r fig.height = 3, fig.width=5}
# bounds for plotting
l_min   <- 0.0           # minimum length for plotting (m)
l_max   <- 0.45          # maximum length for plotting (m)
w_min   <- 1             # minimum mortality rate for plotting (d-1)
w_max   <- 2000          # maximum mortality rate for plotting (d-1)
  
# prepare data frame to display RS ratio
res <- GetScenario_new(1)

vec_age <- seq(from = 0, to = max_age_days, by = 1)
df_RS   <- tibble(
	Age = vec_age, 
	RSratio = sapply(vec_age, FUN = RSRatio)
)

p1 <- ggplot(df_RS, aes(x = Age, y = RSratio)) + 
	geom_line() + 
  ylim(0,rs_max) + 
	labs(
	  x = "Age (days)", 
	  y = "Ratio (Reserve:Structure)", 
    subtitle = "Strategy: desired R:S ratio"
	) +
  theme_bw()
```

```{r}
# prepare data frame to display survival curve
vec_length <- seq(from = l_min, to = l_max, length.out = 101)
df_Length <- tibble(
	Length = vec_length, 
	Prob = mortProb(vec_length)
)
df_Length <- mutate(df_Length, Survive_Y = 1.0/(Prob*365.0))


p2 <- ggplot(df_Length, aes(x = Length, y = Survive_Y)) + 
	geom_line() + 
	labs(
	  x = "Length (m)", 
	  y = "Expected survival (y)", 
    subtitle = "Starvation independent survivorship"
	) +
	theme_bw()
```

```{r}
# prepare data frame to display reproductive costs
vec_weight <- seq(from = w_min, to = w_max, length.out = 101)
df_weight <- tibble(
	Weight = vec_weight, 
	Cost = reproCost(vec_weight)
)

p3 <- ggplot(df_weight, aes(x = Weight, y = Cost)) + 
	geom_line() + 
  geom_abline(intercept = 0, slope = 1, color = "grey") +
	labs(
	  x = "Structural weight (g)", 
	  y = "Reproductive cost (g)", 
    subtitle = "Reproduction cost (non-spawn mass)"
	) +
	theme_bw()
```

```{r fig.width = 9, fig.height = 4}
plot_grid(p1, p2, p3, ncol = 3)
```

### Growth (Length)

# make growth plot dataframe

```{r}
param_value <- NULL
param_type  <- NULL
age         <- NULL
scenario    <- NULL
baseline    <- NULL

# create a large age-length relation for each scenario
for (aa in 1: nscen_used) { # for each scenario
  for (yr in 1:max_age_years) { # for each year
    param_value <- c(param_value, Str[yr, ,aa] + Res[yr, , aa]) # save reserves
    age         <- c(age, 1:365 + 365*(yr-1))            # add next year
    param_type  <- c(param_type, rep("Mass", 365)) # add parameter
    scenario    <- c(scenario, rep(scen_used$Sc_int[aa],365))              # add scenario
  }
}

# place values into a data frame
df_mass <- tibble(
	age = age, 
	type = param_type, 
	value = param_value, 
	scenario = scenario
) %>%
left_join(df_scenario, by = "scenario")

df_mass$maturation_age <- factor(df_mass$maturation_age)

# create a reference data set and scenario data set
df_baseline_mass <- filter(df_mass, scenario == "1") %>%
	dplyr::select(-scenario)
df_other_mass    <- filter(df_mass, scenario != "1")
names(df_other_mass)[4] <- "Sc_int"
df_other_mass <- left_join(df_other_mass, scen_used, by = "Sc_int")
rm(df_mass) # don't need this now
```

# growth in all scenarios

## by length

```{r fig.width=9, fig.height=6}
# colour by age at maturation
ggplot() + 
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(data = df_other, 
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = df_baseline, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Length (m)",
  	color = "Age at\nmaturation (y)",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
	# scale_y_log10() +
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

## by weight

```{r fig.width=9, fig.height=6}
# colour by age at maturation
ggplot() + 
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(data = df_other_mass, 
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = df_baseline_mass, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Weight (g)",
  	color = "Age at\nmaturation (y)",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
	scale_y_log10() +
  facet_wrap( ~ Sc_new, ncol = 6) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

## 4 scenarios length 

```{r}
# colour by age at maturation
ggplot() + 
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(data = filter(df_other, Sc_new %in% c(4,15,17,28)),
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = df_baseline, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Length (m)",
  	color = "Age at\nmaturation (y)"
  ) + 
	# scale_y_log10() +
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )
```

## 4 scenarios weight 

```{r}
# colour by age at maturation
p1 <- ggplot() + 
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(data = filter(df_other_mass, Sc_new %in% c(4,15,17,28)),
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = df_baseline_mass, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Weight (g)",
  	color = "Age at\nmaturation (y)"
  ) + 
	scale_y_log10() +
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )

# colour by age at maturation
p2 <- ggplot() + 
  scale_color_manual(values = c("#ef8a62","#67a9cf")) +
  geom_line(data = filter(df_other_mass, Sc_new %in% c(4,15,17,28), age < 3*365),
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = filter(df_baseline_mass, age < 3*365),
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Weight (g)",
  	color = "Age at\nmaturation (y)"
  ) + 
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )

plot_grid(p1, p2, labels = c("A", "B"), ncol = 1)
```

## all sceanarios weight non logged

```{r fig.width=9, fig.height=6}
# colour by age at maturation
ggplot() + 
  geom_line(data = df_other_mass, 
  	aes(x = age, y = value, color = maturation_age), size = 1) +
  geom_line(data = df_baseline_mass, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Mass (g)",
  	color = "Age at\nmaturation (y)",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
	# scale_y_log10() +
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

### growth in all sc: by Em>Ei

```{r fig.width=9, fig.height=6}
# colour by Em > Ei
ggplot() + 
  geom_line(data = df_other, 
  	aes(x = age, y = value, color = Em_gt_Ei), size = 1) +
  geom_line(data = df_baseline, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Length (m)",
  	color = "Em > Ei",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
  facet_wrap( ~ Sc_new) +   
	# scale_y_log10() +
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

### growth in all sc: by cm>ci 

```{r fig.width=9, fig.height=6}
# colour by cm > ci
ggplot() + 
  geom_line(data = df_other, 
  	aes(x = age, y = value, color = cm_gt_ci), size = 1) +
  geom_line(data = df_baseline, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
	# scale_y_log10() +
  labs(
  	x ="Age (d)",
	  y = "Length (m)",
  	color = "cm > ci",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

### growth in all sc: by m1

```{r fig.width=9, fig.height=6}
# colour by m1
ggplot() + 
  geom_line(data = df_other, 
  	aes(x = age, y = value, color = m1), size = 1) +
  geom_line(data = df_baseline, 
  	aes(x = age, y = value), color = "black", size = 0.5) + 
  labs(
  	x ="Age (d)",
	  y = "Length (m)",
  	color = "m1",
  	subtitle = "Black is baseline, coloured is scenario"
  ) + 
	# scale_y_log10() +
  facet_wrap( ~ Sc_new) +   
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )
```

### ### 
# Export summary values

```{r}
# 1 - juvenile growth - as length and Wgt after 1 and 2 years
Length_1y <- dayPredatorLength[1,364,]*100
Length_2y <- dayPredatorLength[2,364,]*100

Wgt_1y <- Str[1,364,] + Res[1,364,]
Wgt_2y <- Str[2,364,] + Res[2,364,]

# 2 - maturation age in years
matur_age <- rep(NA, times = nscen_used)
for (i in 1:nscen_used) {
  matur_age[i] <- min(which(yearSpawn[ ,i] > 0))
}

# 3 - maturation length 
matur_length <- rep(NA, times = nscen_used)
for (i in 1:nscen_used) {
  matur_length[i] <- dayPredatorLength[matur_age[i],364,i]*100
}

# 4 - adults size - Length and weight at 8, 10, 15y 
Length_5y  <- dayPredatorLength[5,364,  ]*100
Length_8y  <- dayPredatorLength[8,364,  ]*100
Length_10y <- dayPredatorLength[10,364, ]*100
Length_15y <- dayPredatorLength[15,364, ]*100
Length_20y <- dayPredatorLength[20,364, ]*100

Wgt_5y  <- Str[5,364,  ] + Res[5, 364, ]
Wgt_8y  <- Str[8,364,  ] + Res[8, 364, ]
Wgt_10y <- Str[10,364, ] + Res[10,364, ]
Wgt_15y <- Str[15,364, ] + Res[15,364, ]
Wgt_20y <- Str[20,364, ] + Res[20,364, ]

# 5 - reproductive output at first reproduction and in year 3
first_spawn <- rep(NA, times = nscen_used)
for (i in 1:nscen_used) {
  first_spawn[i] <- yearSpawn[matur_age[i],i]
}

spawn_year3 <- yearSpawn[3, ]

# total fitness 
totalFitness <- apply(yearFitness, 2, sum) 

# combine into one dataframe
result_data <- as.data.frame(cbind(
	Length_1y, Length_2y, Length_5y, Length_8y, Length_10y, Length_15y, Length_20y,
	matur_length, matur_age, 
	Wgt_1y, Wgt_2y,Wgt_5y, Wgt_8y, Wgt_10y, Wgt_15y, Wgt_20y, 
	first_spawn, spawn_year3, totalFitness)
)

result_scaled <- result_data
for (i in 1:ncol(result_scaled)) {
  for (j in 2:nrow(result_scaled)) {
    result_scaled[[i]][j] <- 	result_scaled[[i]][j] / result_scaled[[i]][1]
  }
}

ratio_names <- names(result_scaled)

result_scaled$scenario <- scen_used$Sc_int

result_scaled <- result_scaled %>%
	left_join(df_scenario, by = "scenario")

plot_scaled <- gather(result_scaled, key = "Parameter", 
  value = "Ratio", 1:(length(ratio_names))) %>%
	filter(scenario != 1)

plot_scaled$Parameter <- factor(plot_scaled$Parameter,
	levels = ratio_names)

plot_scaled$scenario <- factor(plot_scaled$scenario)

#write.csv(result_scaled, file = "result_scaled.csv")
```

convert ggplot, make a data frame to add scenario parameters?
color = cm < ci, cm = ci, cm > ci 
shape = maturation age (2)
size = m1 (slope) 1,2,4,6,8,20 (8 or 10 gives TSR) fewer sizes (grouped)?

# Fig. 1: allocation strategies

```{r}
df_plot <- scen_par %>%
  filter(Sc %in% scen_used$Sc) %>%
  arrange(Sc)

df_scenario <- df_scenario %>% 
  mutate(Sc = paste("Sc", as.character(scenario), sep = "")) %>%
  arrange(Sc)

df_plot$maturation_age <- factor(df_scenario$maturation_age)

# create some useful summary statistics
df_plot <- df_plot %>%
	mutate(
		Em_gt_Ei = ifelse(Em == Ei, "eq", 
		  ifelse(Em > Ei, "gt", "lt")),
		cm_gt_ci = ifelse(cm == ci, "AM=AI", 
		  ifelse(cm > ci, "AM>AI", "AM<AI")),
	  m1_F = ifelse(m1 == 8, "=8", 
	    ifelse(m1 >8, ">8", "<8"))
	)

df_plot$Em_gt_Ei <- factor(df_plot$Em_gt_Ei, 
  levels = c("lt", "eq", "gt"))
df_plot$cm_gt_ci <- factor(df_plot$cm_gt_ci, 
  levels = c("AM<AI", "AM=AI", "AM>AI"))
df_plot$m1_F <- factor(df_plot$m1_F, 
  levels = c("<8", "=8", ">8"))

p1 <- ggplot(df_plot) +
  scale_shape_manual(values = c(1,19)) +
  scale_size_manual(values = c(1,2,4)) +
  scale_color_manual(values = c("#1b9e77", "#d95f02", "#7570b3")) +
  geom_point(aes(x = a_bar, y = w, color = cm_gt_ci, 
    shape = maturation_age, size = m1_F)) +
  labs(
    x = "Age (days) at 50% allocation to R pool", 
    y = "Proportion of reserves allocated to reproduction, w",
    shape = "Age at\nmaturity (y)",
    color = "Size\nscaling",
    size = "Length-dependent\nvulnerability, zP"
  ) + 
  theme_bw() + 
  theme(
    legend.position="none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )

p2 <- ggplot(df_plot) +
  scale_shape_manual(values = c(1,19)) +
  scale_size_manual(values = c(1,2,4)) +
  scale_color_manual(values = c("#1b9e77", "#d95f02", "#7570b3")) +
  geom_point(aes(x = a_bar, y = rs1, color = cm_gt_ci, 
    shape = maturation_age, size = m1_F)) +
  labs(
    x = "Age (days) at 50% allocation to R pool", 
    y = "Age-dependent transition to reserve allocation, r",
    shape = "Age at\nmaturity (y)",
    color = "Size\nscaling",
    size = "Length-dependent\nvulnerability, zP"
  ) + 
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )

plot_grid(p1, p2, labels = c("A", "B"), rel_widths = c(1, 1.6))
```

## natural mortality

```{r}
# Methods based
scenMort <- c(1, 10:13) # scenarios where only mortality changes
# Add scenarios 10:13 with change in m_min

# Plot base scenario (Eq, 3a)
plot(
  x = dayPredatorLength[1,-1,scenMort[1]], 
  y = natmortality[1,-1,scenMort[1]], 
  type = 'l', ylim = c(0, 0.01), 
  xlab = "Length, m", ylab = "Daily mortality")

# add scenarios: 
# only plots first year: extend to 10 years and look for convergence
for (i in 2:length(scenMort)) {
  points(
    x = dayPredatorLength[1,-1,scenMort[i]],
    y = natmortality[1,-1,scenMort[i]], 
    type = 'l',col = 'red')
}
```

## Population growth rate

```{r}
#to calcualte average generation time we need to do sum(survX * reprX * X)

#reset back to original values, as some plots used smaller ranges
max_age_years = 20


upperTerm <- array(data=0,c(max_age_years, nscen_used))

for (b in 1:nscen_used) {
for (i in 1:max_age_years) {
  upperTerm[i, b] <- daySurvival[i, 365, b] * yearSpawn[i,b] * i
  
}
}


upperTermSc <- apply(upperTerm, 2, sum)
v_LifetimeFitness
Gen_sc <- upperTermSc/v_LifetimeFitness

popGrRate <- log(v_LifetimeFitness)/Gen_sc

scen_used$r0 <- popGrRate
goodOnes <- c(4, 14, 15, 16, 17, 18, 19, 28, 29, 32)

plot(scen_used$Sc_new, scen_used$r0, xlab ="Scenario number", ylab = "Population growth rate, r0")
points(scen_used$Sc_new[goodOnes], scen_used$r0[goodOnes], pch = 19, col = 'red')

abline(h= scen_used$r0[1])
abline(v = c(13.5, 16.5, 26.5, 33.5), lty =2)


```

